---
title: "Answer Key to HW3"
output:
  word_document: default
  pdf_document: default
---

# Properties of Confidence

(a) Suppose that $conf(A \rightarrow B) = c_1$, $conf(A \rightarrow BC) = c_2$, $conf(AC \rightarrow B) = c_3$, respectively. 
Which rule has the lowest confidence?

## Answer:

>>First, we show that $c_2 \leq c_3$: (or due to anti-monotone property)
>>$c_2=conf(A \rightarrow BC) =\sigma(ABC)/\sigma(A)$,
$c_3=conf(AC \rightarrow B) =\sigma(ABC)/\sigma(AC)$,
and $\sigma(A) \ge \sigma(AC)$

>>Second, we show that $c_2 \leq c_1$: 
>>$c_2=conf(A \rightarrow BC) =\sigma(ABC)/\sigma(A)$,
$c_1=conf(A \rightarrow B) =\sigma(AB)/\sigma(A)$
and $\sigma(AB) \ge \sigma(ABC)$

>>Therefore, rule $c_2$ has the lowest confidence. 

(b) For the above question, if these rules have the same support, which rule has the highest confidence?

## Answer:

>>First, $c_2 \leq c_3$ as shown above. 

>>Second, we show that $c_1=c_2$: Since $supp(A \rightarrow B) = supp(A \rightarrow BC)$, 
$\sigma(AB) = \sigma(ABC)$.
Then $\sigma(AB)/\sigma(A) = \sigma(ABC)/\sigma(A)$,
which means $conf(A \rightarrow B) = conf(A \rightarrow BC)$.  

>>Therefore, rule $c_3$ has the highest confidence. 

# Cosmetics Purchases

A drug store chain wants to learn more about cosmetics buyers purchase patterns.  
Specifically, they want to know what items are purchased in conjunction with each other, 
for purposes of display, point of sale special offers, and to 
eventually implement a real time recommender system to cross-sell items at time of purchase.

The cosmetics purchases dataset has the purchase records saved in the form of a matrix.
More specifically, each column represents a product group, and each row a customer transaction.

```{r}
setwd("C:\\UTK\\Data Mining")
data <- read.csv("Cosmetics.csv", row.names = 1)
head(data, 3) # a few sample lines
```

Consider the follwoing association rules found from the data. Answer the few questions that follow.
```{r}
# Rule # Conf. (%)       Antecedent (a)        Consequent (c) Support Count (a) Support Count (c) Support Count (a U c) Lift Ratio 
#      2     60.19 Bronzer, Nail Polish => Brushes, Concealer               103                77                  62     3.908713
```

(1) Explain the "Conf. (%)" output and how it is calculated.

## Answer:

>> "Conf. (%)" is the confidence of a rule. 
In this question, it means $60.19%$ people who bought Bronzer and Nail Polish also bought Brushes and Concealer. It is calculated by the number of transactions having {Bronzer, Nail Polish ,Brushes, Concealer} divided by the number of transactions having {Bronzer, Nail Polish}, i.e., $62 / 103$ = $0.6019$.


(2) Explain the "Support Count ($a$), Support Count ($c$) and Support Count ($a \cup c$)" output and how they are calculated.

## Answer:
>> $a  =103$ means there are $103$ transactions in which people only bought $\{Bronzer, Nail Polish\}$.
>> $c = 77$ means there are $77$ transactions in which people only bought $\{Brushes, Concealer\}$ .
>> $a \cup c = 103$ means there are $62$ transactions in which people bought both $\{Bronzer, Nail Polish\}$ and $\{Brushes, Concealer\}$.
>> They are calculated by scanning the whole dataset. Or, they can be calculated by support times the total number of transactions. 



(3) Explain the "Lift Ratio" and how it is calculated.

## Answer:
>> Lift ratio is to measure the statistical dependence. It measures performance of the new model $P(\{Bronzer, Nail.Polish\} | \{Brushes, Concealer\})$ compared with the base model $P(\{Bronzer, Nail.Polish\})$. It is calculated by their ratio, i.e., $P(\{Bronzer, Nail.Polish\} | \{Brushes, Concealer\}) / P(\{Bronzer, Nail.Polish\})$. The lift ratio is $3.909$ means $\{Brushes, Concealer\}$ and $\{Bronzer, Nail.Polish\}$ are positively corelated and the performance is improved by $3.909$ times after using the new model. 


(4) Explain the rule in words considering the real-world interpretations. 

## Answer:
>>The rule means people who bought Bronzer and Nail Polish also bought Brushes and Concealer. The meausres of this rule have been explained in previous questions.

(5) Based on a subset of 500 cosmetic purchase transactions, 
suppose that we find the following rule: 

$\{Bronzer, Nail Polish\} \rightarrow \{Brushes, Concealer\}$

Suppose further that we find: 

$\sigma(\{Bronzer, Nail Polish\}) = 103$

$\sigma(\{Brushes, Concealer\}) = 77$

$\sigma(\{Bronzer, Nail Polish, Brushes, Concealer\}) = 62$

where $\sigma(X)$ represents the support count for a given itemset $X$. 
Find the confidence and lift of the rule found. 
Interpret these values in context. 

## Answer:

>>$Confidence({Bronzer,NailPolish}\rightarrow{Brushes,Concealer})
=(Support({Bronzer,NailPolish,Brushes,Concealer}))/(Support({Bronzer,NailPolish}))
=62/103=0.602$

>>$Lift({Bronzer,NailPolish}\rightarrow{Brushes,Concealer})
=(Confidence(Bronzer,NailPolish,Brushes,Concealer))/(Support(Bronzer,NailPolish))
=(62/103)/(77/500)=3.909$

>>For a customer who buys Bronzer and Nail Polish, there is $60.2%$ chance that she will buy Brushes and Concealer as well. Knowing that a customer buys Bronzer and Nail Polish will increase the chance of buying Brushes and Concealer by a factor of $3.909$.
