---
title: "Breakfast Cereals (40 Points)"
output: html_document
Name: "Student Name"
---

> The dataset `Cereals` includes nutritional information, store display, and consumer ratings for 77 breakfast cereals.

> a). Remove all cereals with missing values. (5 points)

```{r}
setwd("C:/UTK/Data Mining")
library(readxl)
cereals <- read_excel("Cereals.xlsx", sheet = 2)
cereals_new <- na.omit(cereals)# removing missing values
```

> b). Apply a k-means algorithm using the most interpretable k. Summarize the clusters. Note: interpretability may be subjective. (10 points)

```{r}
set.seed(123)
fit <- kmeans(cereals_new[,4:16], 3)
fit$center  # centers of each variable
fit$cluster # cluster ID for each observation

```

> c). Which cluster do you find the most insightful/interesting? (5 points)

```{r}
###This is a subjective question. You may claim that, for example, Cluster 1 has the highest fat and sugars, which may be unhealthier than the other two clusters.
```

> d). Take a more comprehensive approach to assess the choice of parameter (i.e., number of clusters). How many clusters would you use following this more objective procedure? (10 points)

```{r}
SSEs <- rep(NA,10) # a vector to store SSEs for different k's
SSEs[1] <- fit$totss # total SSE if no clustering is done
# determining number of clusters with SSE
for(k in 2:10){
	fit <- kmeans(cereals_new[,4:16],k)
	SSEs[k] <- fit$tot.withinss
}
par(mar=c(4,4,1,1))
plot(1:10,SSEs,type="b",xlab="Number of Clusters")
```

> e). The elementary public schools would like to choose a set of cereals to include in their daily cafeterias. Every day a different cereal is offered, but all cereals should support a healthy diet. For this goal you are requested to find a cluster of "healthy cereals." How should the data be preprocessed to achieve your goal? (10 points)

```{r}
### The school may set limits on the observations before clustering, namely, max calories, min protein, low fat, low sugar...
###For example, one step you may do is filting the observations with no more than 9 grams of sugar:
cereals_new<- cereals_new[-which(cereals_new$sugars>9),]
```




